Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-18 VMCAI-revised-version/final.tex
What to do with pred-basis-effectivity in case Safe is downward closed?

\begin{theorem}\label{downward srp}
{\sc State-resilience} is decidable for $\post$-effective, $\post$-ideal-effective and effective $\pred$-basis WSTS with downward and upward compatibilities
and $\Safe = \downarrow \Safe$.
\end{theorem}

@@

Procedure 1 enumerates every downward closed subsets in some fixed order $D_1$ , $D_2$ , $\ldots$ by their ideal decomposition. The computability of the enumeration comes from the hypothesis that $\leq$ is ideally-effective (Lemma~4.3. from \cite{DBLP:journals/lmcs/BlondinFM17}).
The procedure then check for every downward closed subset $D_i$ whether $\downarrow \post^*(D_i) \subseteq D_i$. 
\alain{on ne peut pas tester $\downarrow \post^*(D_i) \subseteq D_i$ sans expliquer pourquoi. L'hypothèse "$\post$-ideal-effective" permet de calculer $\downarrow \post(D_i)$. Il manquait la $\post$-effective dans les hypothèses}
Every subset $D_i$ such that $\downarrow \post^*(D_i) \subseteq D_i$ is an “over-approximation” of $\downarrow \post^*(s)$ if it contains $s$.
Notice that, by 
upward compatibility, $\downarrow \post^*(s)$ is such a subset and may eventually be found.

Procedure 1 stops when it finds a subset $D$ such that
$\downarrow \post^*(D) \subseteq D$,
$s \in D$ and
$D   \subseteq \pred^*(\Safe)$. 
Indeed
$D \subseteq  \pred^*(\Safe)$ implies
$\downarrow \post^*(s)  \subseteq  \pred^*(\Safe)$
since $ \downarrow \post^*(s)  \subseteq D$.

@@

Strong downward compatibility implies furthermore the decidability
of {\sc $k$-state-resilience} and {\sc bounded-state-resilience}.
\alain{trop rapide}

>>>>

\begin{theorem}\label{downward srp}
{\sc State-resilience} is decidable for $\post$-effective, $\pred$-basis-effective, $\post$-ideal-effective  WSTS with downward and upward compatibilities
and $\Safe = \downarrow \Safe$.
\end{theorem}

@@

Procedure 1 enumerates every downward closed subsets in some fixed order $D_1$ , $D_2$ , $\ldots$ by their ideal decomposition. The computability of the enumeration comes from the hypothesis that $\leq$ is ideally-effective (Lemma~4.3. from \cite{DBLP:journals/lmcs/BlondinFM17}).
The procedure then checks for every downward closed subset $D_i$ whether $\downarrow \post^*(D_i) \subseteq D_i$. 
\alain{on ne peut pas tester $\downarrow \post^*(D_i) \subseteq D_i$ sans expliquer pourquoi. L'hypothèse "$\post$-ideal-effective" permet de calculer $\downarrow \post(D_i)$. Il manquait la $\post$-effective dans les hypothèses}
Every subset $D_i$ such that $\downarrow \post^*(D_i) \subseteq D_i$ is an “over-approximation” of $\downarrow \post^*(s)$ if it contains $s$.
Notice that, by 
upward compatibility, $\downarrow \post^*(s)$ is such a subset and may eventually be found.

Procedure 1 stops when it finds a subset $D$ such that
$\downarrow \post^*(D) \subseteq D$,
$s \in D$ and
$D   \subseteq \pred^*(\Safe)$. 
\mathieu{ici $\pred^*(\Safe)$ est downward-closed. du coup pas sur que la $\pred$-basis-effectivité telle qu'elle est actuellement nous permette de trancher ... à moins que les hypothèses d'effectivté sur les idéaux nous permettent de guarantir qu'on puisse calculer le $\pred$ d'un idéal ?}
Indeed
$D \subseteq  \pred^*(\Safe)$ implies
$\downarrow \post^*(s)  \subseteq  \pred^*(\Safe)$
since $ \downarrow \post^*(s)  \subseteq D$.

@@

Strong downward compatibility implies furthermore the decidability
of {\sc $k$-state-resilience} and {\sc bounded-state-resilience}.
\alain{trop rapide}
Indeed, with strong downward compatibility, 
$\pred^{\leq k}(\Safe)$ is downward-closed when $\Safe$ is,
and becomes possible to represent \mathieu{... and compute ?} and compare
$\pred^{\leq k}(\Safe)$ 
to other downward closed subsets.
